---
title: "PB Management Analysis"
output: html_document
author: "Cesar O. Estien, Annemarie van der Marel, & Elizabeth Hobson"
editor_options: 
  chunk_output_type: console
---

```{r setup, eval = TRUE, echo = FALSE}

knitr::opts_knit$set(root.dir = "~/Desktop/Field Work Folders/Hobson Lab/Data/", echo = TRUE, eval = FALSE)

```

The purpose of this script is to investigate which auditory cues (hawk, parakeet, or dove calls ) generate stronger behavioral responses which may be useful for management.

Setup:

```{r import-data, eval=TRUE, message=FALSE}
##setwd and path
setwd("~/Desktop/Field Work Folders/Hobson Lab/Data/")
path <- "/Desktop/Field Work Folders/Hobson Lab/Data/"

#install packages needed
X <- c("cowplot", "readr", "ggplot2", "viridis",  "dplyr", "lavaan", "ordinal", "smooth", "Hmisc",  "emmeans", "ggsignif", "car", "olsrr", "ggpubr", "grid", "lubridate", "Rmisc", "plyr", "tidyverse", "RColorBrewer", "reshape2", "cowplot", "egg", "grid", "MASS", "performance", "see", "AICcmodavg", "stargazer", "piecewiseSEM", "lme4", "lmtest", "emmeans")
if (length(setdiff(X, rownames(installed.packages()))) > 0) {
  install.packages(setdiff(X, rownames(installed.packages())))
}

#load packages
invisible(lapply(X, library, character.only = TRUE))

#read datasheet into R
raw_data <- read.csv("long_repulsion_playback_results.csv", header = T) #original data frame

#Clean up raw data file by removing unneeded data
filt_data <- raw_data %>%
  filter(trial != "pilot") %>%
  dplyr::select(c(trial, playback, group_response, latency_majority, speaker_loc, observer_group_response, observer_blind))

#add exemplar and call type to the data frame
pbrepulsion <- read.csv("pb_results.csv") %>% 
  dplyr::select(trial, playback, call_cat, exemplar) #select these columns and storm theme in a new df

#change trial a to factor
pbrepulsion$trial <- as.factor(pbrepulsion$trial) 

#join data frames
repulsion <- left_join(filt_data, pbrepulsion,
                       by=c("trial", "playback")) 
```
## Reformat the Data

Based on the paper format and audience as well, we will collapse invasive and native calls into a "parakeet" column. So, lets reformat the data frame by collapsing invasive and native into one column under "conspecific"

For plotting group_response, we only want to keep those that were seen from the high blind. So let's create a subset with only observations from the high blind.

We want to average the latency majority between the observations and put that in a single data frame, then combine that new average LM with the high_blind df

```{r reformat-data}

#look for 'native' and 'invasive' and replace it with 'conspecific'
repulsion[repulsion == 'native' | repulsion == 'invasive'] <- 'conspecific'

##create a subset of data with high blind observations only
high_gr <- repulsion %>%
  filter(str_detect(observer_blind, "w_high|e_high"))

#average latency between observers into a data frame
avg_lm <- aggregate(latency_majority ~ trial + playback, repulsion, mean)

#take this lm and put it into high_gr. we need to bind the data frames
final_df <- merge(high_gr, avg_lm, by = c('trial', 'playback'))

#lets also remove the latency majority that's there to prevent confusion
final_df <- subset(final_df, select = -(latency_majority.x))

#rename avg_latency to latency majority so i don't have to change aspects of future code
names(final_df)[9] <- "latency_majority"

#In the interest of trying to explore figures that show dispersal-flocking more explicitly, lets create a new column called "Flight Score". -1 = Flocking, 1 = Dispersal, +/- .5 = half-flock/half-dispersal, and 0 are other behaviors (none, vigilant, and minor movement)

#create a new column for flight score
final_df$flight_score <- final_df$group_response
 
#Create rules that convert group responses scores into a scale that goes from -1 to 1
final_df$flight_score <- case_when(
  (final_df$call_cat == "conspecific" & final_df$flight_score == 3) ~ (-.5),
  final_df$flight_score < 3 ~ 0,
  final_df$flight_score == 3 ~ .5,
  final_df$flight_score == 4 ~ 1)

#create new data frame to for mean
bird_mean <- aggregate(latency_majority ~ call_cat, final_df, mean)

#get standard deviation for latency for each call category
sd(final_df$latency_majority, na.rm = TRUE)
bird_sd <- by(final_df$latency_majority, final_df$call_cat, sd)

#lets create median for ordinal data since that is better than the mean
flight_median <- aggregate(flight_score ~ call_cat, final_df, median)
group_median <- aggregate(group_response ~ call_cat, final_df, median)

##Yay!! Let's have control be the one closest to 0 now
repulsion$call_cat <- factor(repulsion$call_cat,levels = c("control", "conspecific", "predator"))
final_df$call_cat <- factor(final_df$call_cat,levels = c("control", "conspecific", "predator"))

#ready!
```
## Visualizing the Data

Lets look at the data again with medians (for ordinal data), means (for continuous data), and a 'conspecific' call category.

We will also visualize flock dynamics more explicitly.

We will add species icons and edit text for legends (e.g., change size) in Adobe Illustrator

```{r new-plots, eval = TRUE}
########################################
#
#
# FIGURE X: A summary figure with everything (call type, latency, group response) on it! 
# (may be supplemental/not use it)
#
#########################################

#start with a basic plot showing the raw data for group response based on categories.
ggplot(final_df, aes(x=call_cat, y=group_response, color= factor(call_cat))) + 
  geom_point() +
  xlab("Playback Treatment") + 
  ylab("Group Response")

#now raw data for latency majority
ggplot(final_df, aes(x=call_cat, y=latency_majority, color= factor(call_cat))) + 
  geom_point() +
  xlab("Playback Treatment") + 
  ylab("Time to Return to Normal Behavior (s)")

#Let's add a box plot and swap the axes.
ggplot(final_df,aes(x=call_cat,y=group_response, fill = call_cat)) +
  geom_boxplot(width = .1, outlier.shape = NA) +
  geom_point(position = position_jitter(width = .15), size = .25) +
  ylab('Group Response') +
  xlab('Call Type') + 
  coord_flip() + 
  theme_cowplot() + 
  guides(fill = FALSE, colour = FALSE) 

#Now lets nest group response into the graph as the shape of points while plotting LM vs call_cat
ggplot(final_df, aes(y=call_cat, x = latency_majority)) + #show raw data
  geom_boxplot(width = .1, outlier.shape = NA, fill = c("#FFF68F", "#C1FFC1", "#FFC1C1")) +
  geom_point(aes(shape = as.factor(group_response), col = call_cat)) + #shape is group response. have to change to factor
  theme_classic() +
  xlim(c(0, 110)) +
  labs(x = "Time to Return to Normal Behavior (s)", y = "Call Type") +
  scale_size(name = "Group Response") +
  scale_colour_manual(guide = "none", 
                      values = c("#CD9B1D", "#008B00", "#8B3A3A")) #change dot colors

#Looks good! Now, we need to edit the legend :)
ggplot(final_df, aes(y=call_cat, x = latency_majority)) + #show raw data
  geom_boxplot(width = .1, outlier.shape = NA, fill = c("#FFF68F", "#C1FFC1", "#FFC1C1")) +
  geom_point(aes(shape = as.factor(group_response), col = call_cat)) + #shape is group response. have to change to factor
  theme_classic() +
  xlim(c(0, 110)) +
  labs(x = "Time to Return to Normal Behavior (s)", y = "Call Type") +
  scale_size(name = "Group Response") +
  scale_colour_manual(guide = FALSE,
                      values = c("#CD9B1D", "#008B00", "#8B3A3A")) + #change dot colors
  scale_shape(name = "Behavioral Response", 
              labels = c("None", "Vigilent", "Minor Movement","Less than 50% Fly","All Birds in Flight"))

##Re-plot it
ggplot(final_df, aes(y=call_cat, x = latency_majority)) + #show raw data
  geom_boxplot(width = .15, outlier.shape = NA, fill = c("#FFF68F", "#C1FFC1", "#FFC1C1")) + #change colors
  geom_point(aes(shape = as.factor(group_response), col = call_cat, alpha = .3)) + #shape is group response (have to change to factor). make points a bit more opaque
  theme_classic() +
  xlim(c(0, 110)) +
  labs(x = "Time to Return to Normal Behavior (s)", y = "Call Type") +
  scale_size(guide = FALSE,
             name = "Group Response") +
  scale_alpha(guide = FALSE) +
  scale_colour_manual(guide = FALSE,
                      values = c("#CD9B1D", "#008B00", "#8B3A3A")) + #change dot colors
  scale_shape(name = "Behavioral Response", 
              labels = c("None", "Vigilent", "Minor Local Movement","50% Fly","All Birds Fly"))

##let's offset the data from the boxplot by using jitter and use colorblind friendly colors
ggplot(final_df, aes(y=latency_majority, x = call_cat)) + #show raw data
  geom_boxplot(width = .1, outlier.shape = NA, fill = c("#9E93B5", "#4D8CF3", "#E3B152"))+
   geom_jitter(aes(shape = as.factor(group_response), col = call_cat, 
                 x = as.numeric(call_cat) + .15, alpha = .2), size = 4, width = .35) +
  theme_classic() +
  ylim(c(-1, 90)) +
  labs(x = "Call Type", y = "Time to Return to Normal Behavior (s)") +
  scale_alpha(guide = FALSE) +
  scale_colour_manual(guide = FALSE,
                      values = c("#9E93B5", "#1F55AE", "#905928")) + #change dot colors
    scale_shape_manual(name = "Behavioral Response", #legend title
      values=c(16, 17, 15, 3, 4), #change shapes
      labels = c("None", "Vigilent", "Minor Movement","Less than 50% Fly","All Birds in Flight")) + #change labels in legend
  coord_flip() # flip x and y axes

#now lets add mean and use geom point instead + add jitter within geom_point
ggplot(final_df, aes(y=latency_majority, x = call_cat)) + #show raw data
  geom_boxplot(width = .1, outlier.shape = NA, fill = c("#9E93B5", "#4D8CF3", "#E3B152"))+
  geom_point(data = bird_mean, shape = 18, size = 7) +
  geom_point(aes(shape = as.factor(group_response), col = call_cat, 
               x = as.numeric(call_cat) + .15, alpha = .2), size = 4, position = position_jitterdodge(dodge.width = 1, jitter.width = 0.6)) + #shape is group response (have to change to factor). make points a bit more opaque 
  theme_classic() +
  ylim(c(-1, 90)) +
  labs(x = "Call Type", y = "Time to Return to Normal Behavior (s)") +
  scale_alpha(guide = FALSE) +
  scale_colour_manual(guide = FALSE,
                      values = c("#9E93B5", "#1F55AE", "#905928")) + #change dot colors
    scale_shape_manual(name = "Behavioral Response", #legend title
      values=c(16, 17, 15, 3, 4), #change shapes
      labels = c("None", "Vigilent", "Minor Movement","50% Birds Fly","All Birds Fly")) + #change labels in legend
  coord_flip() 

###good summary plot for everything! maybe fix the shapes for responses.
###likely won't use but good to have

########################################################
#
#
# FIGURE X: Now, lets do call_cat vs group response and call_cat vs latency majority.
# We're going to combine the same x-axis and flip it so it's shown on the y-axis.
#
#
###########################################################

#plot the graphs we want individually first.

##First latency_majority
plot1 <- ggplot(final_df, aes(x=call_cat, y = latency_majority)) + #show raw data
  geom_boxplot(width = .1, outlier.shape = NA, fill = c("#9E93B5", "#4D8CF3", "#E3B152")) +
  geom_point(aes(col = call_cat, alpha = .1, x = as.numeric(call_cat) + .15, size = 4), position = position_jitterdodge(dodge.width = 1, jitter.width = 0.5)) + #make points a bit more opaque, offset points
  geom_point(data = bird_mean, shape = 18, size = 7) +
  theme_classic() +
  ylim(c(-1, 90)) +
  labs(y = "Time to Return to Normal Behavior (s)") + #, x = "Call Type") +
     theme(axis.text.y = element_blank(), #take away text, title, and ticks
        axis.ticks.y = element_blank(),
        axis.title.y = element_blank()) +
  scale_alpha(guide = FALSE) +
  scale_size(guide = FALSE) +
  scale_colour_manual(guide = FALSE,
                      #name = "Call Type",
                      values = c("#9E93B5", "#1F55AE", "#905928")) + #change dot colors
  coord_flip()
plot1

##Then Group Response
plot2 <- ggplot(final_df, aes(x=call_cat, y = group_response)) + #show raw data
  geom_boxplot(width = .1, outlier.shape = NA, fill = c("#9E93B5", "#4D8CF3", "#E3B152")) +
  geom_point(aes(col = call_cat, alpha = .1, x = as.numeric(call_cat) + .15, size = 4), position = position_jitterdodge(dodge.width = 1, jitter.width = 0.6)) + #make points a bit more opaque, bigger, and offset
  geom_point(data = group_median, shape = 18, size = 7) + #add median instead of mean
  theme_classic() +
  labs(y = "Group Response" ,  y = "Call Type") +
    #theme(axis.text.y = element_blank(), #take away text, title, and ticks
     #   axis.ticks.y = element_blank(),
      #  axis.title.y = element_blank()) +
  scale_alpha(guide = FALSE) +
  scale_size(guide = FALSE) +
  scale_colour_manual( guide = FALSE,
    #name = "Call Type",
    values = c("#9E93B5", "#1F55AE", "#905928")) +
     coord_flip()
plot2

#Now, we need to combine them!
cowplot::plot_grid(plot2, plot1, align = "h", ncol = 1)
egg::ggarrange(plot2, plot1, widths = c(1, 1)) 

############################################
#
#
# Figure S1: Habituation Figure; Plot Group Responses over Trials
#
#
############################################

#graph behavioral responses on y axis and trials on x, with playback type plotted in color and shape to see if the response diminished over time

ggplot(final_df, aes(y=as.numeric(group_response), x = as.numeric(trial))) + #show raw data
   geom_point(aes(col = call_cat, shape = call_cat, alpha = 0.1, size = 9), position = position_jitterdodge(dodge.width = .5, jitter.width = 0.6))  + #shape is group response (have to change to factor). make points a bit more opaque 
  geom_smooth(aes(col = call_cat),
              method = "lm",
              se = FALSE) +
  theme_classic() +
  labs(x = "Trial", y = "Group Response") +
  scale_alpha(guide = FALSE) +
  scale_size(guide = FALSE) +
  scale_colour_manual(name = "Call Type",
                      values = c("#9E93B5", "#1F55AE", "#905928")) #change dot colors

############################################
#
#
# Figure S2: Habituation Figure; Plot Latency over Trials
#
#
############################################

#graph behavioral responses on y axis and trials on x, with playback type plotted in color and shape to see if the response diminished over time

ggplot(final_df, aes(y=latency_majority, x = as.numeric(trial))) + #show raw data
   geom_point(aes(col = call_cat, shape = call_cat, alpha = 0.1, size = 9), position = position_jitterdodge(dodge.width = .5, jitter.width = 0.6))  + #shape is group response (have to change to factor). make points a bit more opaque 
  geom_smooth(aes(col = call_cat),
              method = "lm",
              se = FALSE) +
  theme_classic() +
  labs(x = "Trial", y = "Time to Return to Normal Behavior (s)") +
  scale_alpha(guide = FALSE) +
  scale_size(guide = FALSE) +
  scale_colour_manual(name = "Call Type",
                      values = c("#9E93B5", "#1F55AE", "#905928")) #change dot colors

###########################################
#
#
# Figure X: Visualize Repulsion and Attraction Behaviors 
#
#
###########################################

#Basic plot 
ggplot(final_df, aes(x = call_cat, y = flight_score)) +
  geom_point(aes(size = 4)) +
  theme_classic() +
  ylim(c(-1.0,1.0)) +
  labs( x = "Call Type", y = "Flock-Dispersal") +
  scale_size(guide = FALSE) +
  scale_colour_manual(name = "Call Type",
                      values = c("#9E93B5", "#1F55AE", "#905928"))

#play with colors, add median, jitter,  and dashed line
ggplot(final_df) +
  aes(x = call_cat, y = flight_score, colour = call_cat) +
   geom_point(aes(alpha = 0.1, size = .5), position = position_jitterdodge(dodge.width = .5, jitter.width = 0.6)) +
  geom_point(data = flight_median, shape = 18, size = 7, color = "black") +
  theme_classic() +
  xlab("Call Type") + 
  ylab("Flight Score") +
  ylim(c(-1.0, 1.0)) +
  geom_hline(yintercept = 0, linetype = 'dashed') + #add dashed line
  scale_color_hue(guide = FALSE) + 
  scale_size(guide = FALSE) +
  scale_alpha(guide = FALSE)

#add boxplots now
ggplot(final_df) +
  aes(x = call_cat, y = flight_score, colour = call_cat) +
  geom_boxplot(width = .1, outlier.shape = NA, fill = c("#9E93B5", "#4D8CF3", "#E3B152")) +
   geom_point(aes(alpha = 0.1, size = .5), position = position_jitterdodge(dodge.width = .5, jitter.width = 0.6)) +
  geom_point(data = flight_median, shape = 18, size = 7, color = "black") +
  theme_classic() +
  xlab("Call Type") + 
  ylab("Flight Score") +
  ylim(c(-1.0, 1.0)) +
  geom_hline(yintercept = 0, linetype = 'dashed') +
  scale_color_hue(guide = FALSE) +
  scale_size(guide = FALSE) +
  scale_colour_manual( guide = FALSE,
    #name = "Call Type",
    values = c("#9E93B5", "#1F55AE", "#905928"))

##Move conspecific to middle, change colors for box plot outline
final_df$call_cat <- factor(final_df$call_cat,levels = c("control", "conspecific", "predator"))

#replot and remove legend
ggplot(final_df, aes(x = call_cat, y = flight_score)) + 
  geom_boxplot(width = .1, outlier.shape = NA, fill = c("#9E93B5", "#4D8CF3", "#E3B152")) +
   geom_point(aes(col = call_cat, alpha = 0.1, size = .5), position = position_jitterdodge(dodge.width = .5, jitter.width = 0.6)) +
  geom_point(data = flight_median, shape = 18, size = 7, color = "black") +
  theme_classic() +
  xlab("Call Type") + 
  ylab("Flight Score") +
  ylim(c(-1.0, 1.0)) +
  geom_hline(yintercept = 0, linetype = 'dashed') +
  scale_alpha(guide = FALSE) +
  scale_color_hue(guide = FALSE) +
  scale_size(guide = FALSE) +
  scale_colour_manual( guide = FALSE,
    #name = "Call Type",
    values = c("#9E93B5", "#1F55AE", "#905928"))

#########################################################
#
#
# Figure X: Behavioral responses as % in bar plots rather than raw data with box plots
#
#
###############################################################

#make stacked bar plot
ggplot(final_df, aes(x = call_cat, y = group_response, fill = group_response)) +
  geom_col(position = "fill") +
  labs(x = "Call Type", y = "Proportion of Group Response") +
  theme_classic() +
  coord_flip()

#add levels so that it plots in order from 0-4
final_df_barplot <- final_df
final_df_barplot$response <- factor(final_df_barplot$group_response, 
       levels = rev(c("0", "1", "2", "3", "4")))
       #labels = c("None", "Vigilent", "Minor Movement", "50% Birds Fly", "All Birds Fly"))

#Final Plot
ggplot(final_df_barplot, aes(x = call_cat, fill = response)) +
  geom_bar(position = "fill") +
  labs(x = "Call Type", y = "Proportion of Group Response") +
  theme_classic() +
  scale_fill_manual(values = c("0" = "#E4E8FF",
                               "1" = "#B0B7E6",
                               "2" = "#6C7BE2",
                               "3" = "#384CDA",
                               "4" = "#0D20A2")) +
  coord_flip()

```
#Model Fitting: 

We will use ordinal package to test group_response and call_cat, linear mixed models for latency, and Kruskal–Wallis to examine significance for flight response.

Due to previous model runs, we know observer has no significant influence so we will remove observer from the model. Additionally, to see if trial has an influence on response and latency, we will remove trial as a random factor and make it a core part of the model. Only exemplar will be a random effect now


```{r Ordinal-Model, eval = TRUE}
########################################
#
##Ordinal Model - Group Response 
#
####################################

#Create a data frame for modeling
repulsion2 <- final_df 

#change variables to factors
repulsion2$exemplar <- as.factor(repulsion2$exemplar)
repulsion2$response <- ordered(repulsion2$group_response) #ordered factor
#reorder levels 
repulsion2$call_cat <- factor(repulsion2$call_cat, levels=c("control", "conspecific", "predator"))

#Run Models
ordinal_1 <- clmm(repulsion2$response ~ repulsion2$call_cat + (1|repulsion2$exemplar))
ordinal_2 <- clmm(repulsion2$response ~ repulsion2$call_cat + repulsion2$trial + (1|repulsion2$exemplar))
ordinal_3 <- clmm(repulsion2$response ~ repulsion2$trial + (1|repulsion2$exemplar))
ordinal_null <- clmm(repulsion2$response ~ 1 + (1|repulsion2$exemplar))

#compare models
AIC(ordinal_1, ordinal_2, ordinal_3, ordinal_null) 

#ordinal 1 is the top model with exemplar as random factor! 
summary(ordinal_1) #trial has no effect, predator is significant

#perform likelihood test on null and selected model
anova(ordinal_1, ordinal_null) #significant. p-value, LR stat

#get confidence intervals
confint(ordinal_1, level = 0.95) #predator is significant 


#Run Tukey to examine significance between call types for group response (#https://rcompanion.org/handbook/G_12.html)

marginal_ord = emmeans(ordinal_1, "call_cat") #define model we're looking at

pairs(marginal_ord,
      adjust="tukey") #run Tukey

#Get R2 values - cannot get R2 from ordinal data. commented out
#rsquared(ordinal_1) 
#rsquared(ordinal_2) 
#rsquared(ordinal_3)
#rsquared(ordinal_null) 

#Make a list of models with name types 
gr_AIC_list <- list(ordinal_1, ordinal_2, ordinal_3, ordinal_null)
gr_model_names <- c("Call Type", "Call Type + Trial", "Trial", "Null")
gr_AIC_table <- aictab(gr_AIC_list, gr_model_names)

#Export
write.csv(gr_AIC_table, "gr_AIC.csv")


####################################
#
# Flight Score: we'll run Kruskal–Wallis one-way analysis of variance 
#
####################################

kruskal.test(flight_score ~ call_cat, data = repulsion2) #significant!

#where is the significance. we'll do a wilcox test
pairwise.wilcox.test(repulsion2$flight_score, repulsion2$call_cat,
                 p.adjust.method = "BH")

```


```{r Linear-Model, eval = TRUE}

########################################
#
# Linear Model - Latency Majority
#
#######################################

#Before we can run models, we need to see what distribution the data follows

#put it in a new data frame
latency_majority.t <- final_df$latency_majority
par(mfrow = c(1,1))

#normal model 
qqp(latency_majority.t, "norm")

#lognormal model
qqp(latency_majority.t, "lnorm") 

#nbinomial model
nbinom <- fitdistr(latency_majority.t, "negative binomial") 
qqp(latency_majority.t, "nbinom", size = nbinom$estimate)

#Poisson
poisson <- fitdistr(latency_majority.t, "Poisson")
qqp(latency_majority.t, "pois", lambda = poisson$estimate) 

#Gamma
gamma <- fitdistr(latency_majority.t, "gamma")
qqp(latency_majority.t, "gamma", shape = gamma$estimate[[1]], rate = gamma$estimate[[2]]) 

#Since it's normally distributed, we can run a linear mixed model instead of a GLMM using the lme4 package

#create models
LM_1 <- lmer(repulsion2$latency_majority ~ repulsion2$call_cat + (1|repulsion2$exemplar))
LM_2 <- lmer(repulsion2$latency_majority ~ repulsion2$call_cat + repulsion2$trial + (1|repulsion2$exemplar))
LM_3 <- lmer(repulsion2$latency_majority ~ repulsion2$trial + (1|repulsion2$exemplar))
LM_null <- lmer(repulsion2$latency_majority ~ 1 + (1|repulsion2$exemplar))

#compare models 
AIC(LM_1, LM_2, LM_3, LM_null) #trial seems to matter since it's in the top model 

#summary of top model
summary(LM_2) #not giving p-value
anova(LM_2)

#perform likelihood tests

#compare top model to null 
anova(LM_2, LM_null)

#is call cat significant? find out by comparing model with call cat to the one without
anova(LM_2, LM_3) #it is!

#let's do the same for trial to see if trial is actually significant
anova(LM_2, LM_1) #it's not

#confidence intervals for top model
confint(LM_2, level = 0.95)

#since there is significance, let's see where it is by using Tukey
marginal_lat = emmeans(LM_2, "call_cat")

pairs(marginal_lat,
      adjust="tukey")

#Get rsquare values
rsquared(LM_1) #0.642909
rsquared(LM_2) #0.7135345
rsquared(LM_3) #.09427292
rsquared(LM_null) #8.433856 x 10^-21

#Make a list of models with name types 
lat_AIC_list <- list(LM_1, LM_2, LM_3, LM_null)
lat_model_names <- c("Call Type", "Call Type + Trial", "Trial", "Null")
lat_AIC_table <- aictab(lat_AIC_list, lat_model_names)

#export
write.csv(lat_AIC_table, "lat_AIC.csv")

#report chi-squared and p-value
#example report of it LR test: Λ = 140.5, P < 0.001)

```
#Use Performance Package

We'll use the performance package to get additional values for models as well as verify the top models.



```{r Model-Check, eval = TRUE}
##################################################
#
# Performance Package: Checking if the models are good!
# we can get a bit more information on each model from this (e.g., weight)
#
#####################################################

#check fo heteroskedasticity (non-constant error variance) because linear models assume homoscedasticity

#lets check
lat_lm_hsktest <- lm(repulsion2$latency_majority ~ repulsion2$call_cat)
check_heteroscedasticity(lat_lm_hsktest) #works!

#compare performance for group response
compare_performance(ordinal_1, ordinal_2, ordinal_3, ordinal_null) 
gr_model_compare_table <- compare_performance(ordinal_1, ordinal_2, ordinal_3, ordinal_null) 

#plot
model_comparison_plot <-plot(compare_performance(ordinal_1, ordinal_2, ordinal_3, ordinal_null, rank = TRUE))
model_comparison_plot

#export
write.csv(gr_model_compare_table, "gr_model_comparison.csv")

#compare performance for latency
compare_performance(LM_1, LM_2, LM_3, LM_null) 
latency_model_compare_table <- compare_performance(LM_1, LM_2, LM_3, LM_null) 
```
#Citations

Export citations

```{r Citations, eval = TRUE}
# Citations
citation("rstatix")
citation("lme4")
citation("car")
citation("MASS")
citation("performance")
citation("ordinal")
citation("ggplot2")
citation("lmtest")
citation("emmeans")
```